\documentclass[11pt]{article}

%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%

\usepackage{url}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{enumerate}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage{amsrefs}
\usepackage[affil-it]{authblk}

%%%%%%%%%%%%%%% TITLE/AUTHOR INFORMATION %%%%%%%%%%%%%%%

\title{Sample MTH 261 Paper}
\author{Damien Adams}
\date{\today}
\affil{Portland Community College}

%%%%%%%%%%%%%%% CUSTOM FORMAT %%%%%%%%%%%%%%%

\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{+.4in}

\setlength{\oddsidemargin}{0.in}
\setlength{\evensidemargin}{0.in}
\setlength{\textwidth}{6.46in}
\setlength{\textheight}{8.4in}

\usepackage[margin=2.5cm]{geometry}

%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\norm}[1]{\left\lvert#1\right\rvert}    % Norm

%%%%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%% TITLE %%%%%%%%%%%%%%%

\maketitle

%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%

\begin{abstract}

This paper seeks to give an example of what a paper might look like and means to be a template for the student's paper. \TeX is not easy to learn, so this is meant to streamline the process. Any technical questions should be Google'd and/or posed to the instructor.
 
\end{abstract}

%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%

This is where you should type your paper. Be sure to write in complete sentences. You should use correct grammar.

When you begin a sentence, it should not begin with a numeral. When you include a figure, it should have a caption.

Begin your paper with an introduction of the problem. Afterwards, explore your topic. When you are finished with your topic, write a conclusion. The last part of your paper should be a bibliography.





%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%

\begin{bibdiv}
\begin{biblist}

%If you cite a book, here is how to cite

 \bib{A}{book}{
  title = {Write the title of the book here},
  author = {Write the author of the book here},
  publisher = {Write the publisher of the book here},
  date = {Write the year the book was published here},
  page = {If you cite a particular page number, or several pages, include them here}
 }
 
 \bib{B}{book}{
  title = {If you use another book, do the same thing as before},
  author = {etc.}
 }
 
\end{biblist}
\end{bibdiv}

%%%%%%%%%%%%%%% END DOCUMENT %%%%%%%%%%%%%%%

\end{document}